Work Fragmentation in Developer Interaction Data

### 2015-08-07 paper.tex
format + discussion, conclusions, threats

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_dur_ratio}
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events_udc}
\end{figure}

Again the hypothesis holds as with Mylyn. We can see on the Figure \ref{fig:box_dur_events_udc} that with short interruptions the metrics are greater than when facing a prolonged one, for more time is needed to recover after a long interruption.

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions on UDC data} %, and editions and selections.}
\label{tbl:p_value2_udc}
\centering
\begin{tabular}{l | p{0.7cm} | p{1.9cm} | p{1.9cm} } 
   & none & short &  prolonged  \\  
  \hline
  \multicolumn{4}{c}{\textbf{Edits}} \\
  \hline
  mean & 3.97 &	2.75 & 1.79 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
   \cline{3-4} 
  U-test & $\hookrightarrow$ &  $<$ 2.6e-12 & $<$ 2.2e-16  \\

@@

The effect size test results on the Table \ref{tbl:p_value2_udc} matches the previous observations on a less pronounced effect. The Cohen's \textit{d} test results tell us that we can label the effect from medium to large and the mean values act accordingly to our hypothesis and conclusions with Mylyn.

\subsection{RQ3: Local relationships between interruptions and productivity}
The sessions with UDC went through the same process of transformation into 10 chunks of equal time. The results on the Figure \ref{fig:bins_int_udc} show the same productivity pattern that we saw before with Mylyn.
\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_without_int_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int1_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int2_med} 
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int_udc}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_dur_ratio}
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events_udc}
\end{figure}
Again the hypothesis holds as with Mylyn. We can see on the Figure \ref{fig:box_dur_events_udc} that with short interruptions the metrics are greater than when facing a prolonged one, for more time is needed to recover after a long interruption. 
\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions on UDC data} %, and editions and selections.}
\label{tbl:p_value2_udc}
\centering
\begin{tabular}{l | p{0.7cm} | p{1.9cm} | p{1.9cm} } 
   & none & short &  prolonged  \\  
  \hline
  \multicolumn{4}{c}{\textbf{Edits}} \\
  \hline
  mean & 3.97 &	2.75 & 1.79 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
   \cline{3-4} 
  U-test & $\hookrightarrow$ &  $<$ 2.6e-12 & $<$ 2.2e-16  \\

@@

\end{tabular}
\end{table}
The effect size test results on the Table \ref{tbl:p_value2_udc} matches the previous observations on a less pronounced effect. The Cohen's \textit{d} test results tell us that we can label the effect from medium to large and the mean values act accordingly to our hypothesis and conclusions with Mylyn.
\subsection{RQ3: Local relationships between interruptions and productivity}
The sessions with UDC went through the same process of transformation into 10 chunks of equal time. The results on the Figure \ref{fig:bins_int_udc} show the same productivity pattern that we saw before with Mylyn.
\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_without_int_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int1_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int2_med} 
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int_udc}
\end{figure}
